Bivariate_analysis on different datasets

### 2018-02-08 All_analysis.Rmd
modified

  ans<-OurBiCopSelect(u1,u2,families,AICBIC="AIC",level=0.05,numBS=4,gofnormal=T)
  if(ans$IndepTestRes<level){
    gfc_numBS<-100
    gfc_p_CvM<-ans$GofRes_CvM
    gfc_p_KS<-ans$GofRes_KS
    gfc_p_CvM_stat<-ans$GofRes_CvM_stat
    gfc_p_KS_stat<-ans$GofRes_KS_stat

@@

    pmin<-min(ans$GofRes_CvM,ans$GofRes_KS,ans$GofRes_Normal_CvM,ans$GofRes_Normal_KS)
    if(pmin<0.2){
      ans2<-OurBiCopSelect(u1,u2,families,AICBIC="AIC",level=0.05,numBS=5,gofnormal=T)
      gfc_numBS<-1000
      gfc_p_CvM<-ans2$GofRes_CvM
      gfc_p_KS<-ans2$GofRes_KS
      gfc_p_CvM_stat<-ans$GofRes_CvM_stat
      gfc_p_KS_stat<-ans$GofRes_KS_stat

@@

```{r loaddatatest, echo=F}
# here you can directly load the bivariate data to the variable d
# or you can save the bivariate data to d after some data extraction
d<-readRDS("givendata.RDS")
```

@@

```{r loaddata1, echo=F}
# here you can directly load the bivariate data to the variable d
# or you can save the bivariate data to d after some data extraction
d<-readRDS("givendata.RDS")
```

>>>>

  ans<-OurBiCopSelect(u1,u2,families,AICBIC="AIC",level=0.05,numBS=100,gofnormal=T)
  if(ans$IndepTestRes<level){
    gfc_numBS<-100
    gfc_p_CvM<-ans$GofRes_CvM
    gfc_p_KS<-ans$GofRes_KS
    gfc_p_CvM_stat<-ans$GofRes_CvM_stat
    gfc_p_KS_stat<-ans$GofRes_KS_stat

@@

    pmin<-min(ans$GofRes_CvM,ans$GofRes_KS,ans$GofRes_Normal_CvM,ans$GofRes_Normal_KS)
    if(pmin<0.2){
      ans2<-OurBiCopSelect(u1,u2,families,AICBIC="AIC",level=0.05,numBS=1000,gofnormal=T)
      gfc_numBS<-1000
      gfc_p_CvM<-ans2$GofRes_CvM
      gfc_p_KS<-ans2$GofRes_KS
      gfc_p_CvM_stat<-ans$GofRes_CvM_stat
      gfc_p_KS_stat<-ans$GofRes_KS_stat

@@

```{r loaddatatest, echo=F}
# here you can directly load the bivariate data to the variable d
# or you can save the bivariate data to d after some data extraction
d<-readRDS("Data/givendata.RDS")
```

@@

```{r loaddata1, echo=F}
# here you can directly load the bivariate data to the variable d
# or you can save the bivariate data to d after some data extraction
d<-readRDS("Data/givendata.RDS")
```
